Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-01 ms.tex
described how I plan to run the crosshatch simulation.

\subsection{Subpixel Crosshatching}
The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
The angle between these lines are 67.60$\degree$, 44.5$\degree$ and 67.8$\degree$.
These are best visualized with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.

@@

We attempt to model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency.
We model the two dimensional Fourier amplitude $f(x',y')$ for one angle as
\begin{equation}
f(x',y') = \exp{\left(-y'^2/\tau_\perp\right)} \left( \frac{a}{b + x'^2} + \frac{c}{1 + \exp{\left( (|x'| - d)/\tau_\parallel \right)} } \right),
\end{equation}
where $x'$ and $y'$ are rotated coordinates, $\tau_\perp$ is the perpendicular exponential constant, $a$ and $b$ are polynomial constants for the central peak of the Fourier plane, $c$ is an exponential amplitude constant and $d$ is the cutoff frequency with an exponential constant $\tau_\parallel$.
For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
\begin{equation}
x' = (x - x_0) \cos{\theta} + (y - y_0) \sin{\theta}
\end{equation}
and
\begin{equation}
y' = -(x - x_0) \sin{\theta} + (y - y_0) \cos{\theta}.
\end{equation}
We include three angles so that the total Fourier amplitude is
\begin{equation}
f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i,y'_i)
\end{equation}
for $\theta_i = 0.9^\circ$, 68.7$^\circ$ and 113.2$^\circ$.

@@

>>>>

\subsection{Subpixel Crosshatching}

\subsubsection{Subpixel Crosshatching Characterization}
The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
The angle between these lines are 67.60$\degree$, 44.5$\degree$ and 67.8$\degree$.
These are best visualized with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.

@@

@@

\subsubsection{Subpixel Crosshatching Simulation}

The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope jitter.
NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}

We simulate the effect of this jitter on NIRCam grism time series observations with the following steps:
\begin{itemize}
	\item Fit the existing flat field to an crosshatch model that describes the subpixel behavior
	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
	\item Jitter the simulated PSF over with a 6 mas Gaussian
	\item Bin the simulated images into the native pixel size
	\item Divide by the flat field
	\item Measure the light curve with photometry or spectroscopic aperture
\end{itemize}

We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency as seen in Figure \ref{fig:crossHatchA5}.
We model the two dimensional Fourier amplitude $f(x',y')$ for one angle as
\begin{equation}
f(x',y') = \exp{\left(-y'^2/\tau_\perp\right)} \left( \frac{a}{b + x'^2} + \frac{c}{1 + \exp{\left( (|x'| - d)/\tau_\parallel \right)} } \right),
\end{equation}
where $x'$ and $y'$ are rotated coordinates, $\tau_\perp$ is the perpendicular exponential constant, $a$ and $b$ are polynomial constants for the central peak of the Fourier plane, $c$ is an exponential amplitude constant and $d$ is the cutoff frequency with an exponential constant $\tau_\parallel$.
For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
\begin{equation}
x' = (x - x_0) \cos{\theta} + (y - y_0) \sin{\theta}
\end{equation}
and
\begin{equation}
y' = -(x - x_0) \sin{\theta} + (y - y_0) \cos{\theta}.
\end{equation}
We include three angles so that the total Fourier amplitude is
\begin{equation}
f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i,y'_i)
\end{equation}
for $\theta_i = 0.9^\circ$, 68.7$^\circ$ and 113.2$^\circ$.
